\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

\pdfgentounicode=1

% Custom list commands
\newcommand{\resumeItem}[1]{\item\small{#1} \vspace{-3pt}}
\newcommand{\resumeSubheading}[4]{%
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubheadingNoItal}[4]{%
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    #3 & #4 \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubheadingSmall}[2]{%
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}, labelsep=0.15in]}
\newcommand{\resumeJustifiedList}{\begin{itemize}[leftmargin=0.3in, label=\textbullet, labelsep=0.1in]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemDash}[1]{\item\small{\hspace{-0.1cm} -- #1} \vspace{-3pt}}

\begin{document}

{\Large
\begin{center}
  \textbf{\Huge Kunal Pai} \\
  \small 408-620-2339 $|$ \href{mailto:pai.kunal05@gmail.com}{pai.kunal05@gmail.com} $|$ 
  \href{https://linkedin.com/in/kunpai}{linkedin.com/in/kunpai} $|$
  \href{https://github.com/kunpai}{github.com/kunpai} $|$
  \href{https://www.kunpai.space}{kunpai.space}
\end{center}
}

\section{Education}
{\normalsize
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
  \item \textbf{M.S., Computer Science}, University of California, Davis (GPA: \textbf{4.0/4.0}) \hfill Expected: June 2026
  \item \textbf{B.S., Computer Science \& Engineering}, University of California, Davis (GPA: \textbf{3.8/4.0}) \hfill June 2023
\end{itemize}
}

\section{Relevant Skills}
{\normalsize
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
  \item \textbf{Languages}: Python, Java, JavaScript, C++, C
  \item \textbf{Web Technologies}: HTML, CSS, DOM, React, Next.js, Django, Flask
  \item \textbf{Tools \& Frameworks}: Git, Docker, MongoDB, Unix/Linux, Jupyter, pandas, NumPy, TensorFlow, PyTorch, Hugging Face
  \item \textbf{Data Science}: Data mining, data visualization, AI, machine learning, natural language processing, multi-agent systems
  \item \textbf{Software Quality}: Testing frameworks, code review practices, continuous integration
  \item \textbf{Methodologies}: Agile development, team collaboration, continuous improvement
\end{itemize}
}

\section{Work Experience}
{\normalsize
\resumeSubHeadingList

  \resumeSubheadingSmall{Graduate Student Researcher, \textit{DArchR Lab @ UC Davis}}{Jun 2023 -- Present}
  \resumeJustifiedList
    \resumeItem{Led development teams across 3+ projects, demonstrating leadership and collaboration skills.}
    \resumeItem{Engineered a high-fidelity Python/C++ gem5 PEA model for superconducting NoCs and accelerators.}
    \resumeItem{Developed simulation methodologies achieving 90\% correlation with hardware performance metrics.}
    \resumeItem{Mentored 5 undergraduate students, contributing to lab publications and research output.}
  \end{itemize}

  \resumeSubheadingSmall{Student Researcher, \textit{DECAL Lab @ UC Davis}}{Sep 2022 -- Dec 2024}
  \resumeJustifiedList
    \resumeItem{Generated comprehensive dataset from 200+ open-source Python repositories, enabling research on code-documentation alignment.}
    \resumeItem{Designed and implemented evaluation pipelines that measured language model calibration for code repair tasks.}
    \resumeItem{Validated large language models' code summarization capability by applying metrics like ROUGE and METEOR.}
  \end{itemize}

  % \resumeSubheadingSmall{Software Developer Intern \& Tech Lead, \textit{humanID, Davis}}{Jan 2022 -- Jun 2022}
  % \resumeJustifiedList
  %   \resumeItem{Led technical implementation of 10+ global projects across teams in 4+ countries.}
  %   \resumeItem{Built Django-based permission management app supporting 100+ active users.}
  %   \resumeItem{Created end-to-end documentation for a Discord bot addressing user verification and spam control.}
  % \end{itemize}

  \resumeSubheadingSmall{Technical Product Marketing Intern, \textit{SiTime Corp., Santa Clara}}{Jul 2021 -- Sep 2021}
  \resumeJustifiedList
    \resumeItem{Presented a strategic business proposal identifying \$250K in potential revenue growth.}
    \resumeItem{Created detailed technical documentation and PRD diagrams.}
    \resumeItem{Conducted market research identifying key optical transceiver customers for targeted outreach.}
  \end{itemize}

\resumeSubHeadingListEnd
}

\section{Publications (Selected)}
{\normalsize
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]

  \resumeItem{\textbf{Title of Publication 1}, Journal Name, Year.}
  \resumeItem{\textbf{Title of Publication 2}, Conference Name, Year.}
  \resumeItem{\textbf{Title of Publication 3}, Journal Name, Year.}
\end{itemize}
}

\section{Project Experience}
{\normalsize
\resumeSubHeadingList

  \resumeSubheading{\href{https://resources.gem5.org/}{gem5 Vision}}{Jan 2023 -- Jun 2023}{Framework}{Next.js, Python, MongoDB, JSON Schema}
  \resumeJustifiedList
    \resumeItem{Built a database-driven web app enabling 20x faster search across 1,200+ resources for 500+ monthly users.}
    \resumeItem{Integrated local and remote JSON file access with MongoDB backend for improved resource retrieval.}
    \resumeItem{Collaborated with peers on design decisions and testing for performance improvements.}
  \end{itemize}

  \resumeSubheading{\href{https://www.kunpai.space/assets/papers/toxicity.pdf}{Effects of Toxicity on Disengagement in Open-Source Projects}}{Jan 2024 -- Mar 2024}{Software Engineering Project}{Python, GitHub mining, scikit-learn}
  \resumeJustifiedList
    \resumeItem{Analyzed developer engagement patterns in open-source repositories using data mining techniques.}
    \resumeItem{Applied sentiment analysis and toxicity metrics to identify factors affecting contributor retention.}
    \resumeItem{Developed a regression model achieving 76\% correlation between community disengagement and project toxicity levels.}
  \end{itemize}

  \resumeSubheading{Automated Frameworks of Semantic Augmentation for Math}{Apr 2024 -- Jun 2024}{Machine Learning Project}{Python, NLP, Prompt Engineering}
  \resumeJustifiedList
    \resumeItem{Improved LLM prompting accuracy by 10\% and fine-tuning accuracy by 40\% for math word problems through automated semantic augmentation frameworks.}
    \resumeItem{Collaborated on developing selection algorithms for higher-quality one-shot prompting examples.}
    \resumeItem{Applied rigorous testing to benchmark model performance improvements.}
  \end{itemize}

\resumeSubHeadingListEnd
}

\end{document}
