\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1} \vspace{-3pt}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Kunal Pai} \\
  \small 408-620-2339 $|$ \href{mailto:pai.kunal05@gmail.com}{pai.kunal05@gmail.com} $|$ 
  \href{https://linkedin.com/in/kunpai}{linkedin.com/in/kunpai} $|$
  \href{https://github.com/kunpai}{github.com/kunpai}
\end{center}

\section{Education}
% \resumeSubHeadingList
%   \resumeSubheading
%     %   {University of California, Davis}{Davis, CA}
%       {M.S., Computer Science, University of California, Davis}{Expected: June 2025}
%       {}{}
%   \resumeSubheading
%     %   {University of California, Davis}{Davis, CA}
%       {B.S., Computer Science \& Engineering, University of California, Davis}{June 2023}
%       {}{}
% \resumeSubHeadingListEnd
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{M.S., Computer Science}, University of California, Davis \hfill Expected: June 2025
    \item \textbf{B.S., Computer Science \& Engineering}, University of California, Davis \hfill June 2023
  \end{itemize} % End the list

% \resumeSubHeadingList
% \resumeSubheading
%       {Spiess, C., Gros, D., \underline{Pai, K.}, Pradel, M., Rabin, MRI, Alipour, A., Jha, S., Devanbu, P., \& Ahmed, T. (2025).}{}
%       {Calibration and Correctness of Language Models for Code}{ICSE 2025.}
%   \resumeSubheading
%       {Ahmed, T., \underline{Pai, K.}, Devanbu, P., \& Barr, E. (2024).}{}
%       {Automatic Semantic Augmentation of Language Model Prompts (for Code Summarization)}{ICSE 2024.}
%       % {Available: \url{https://www.computer.org/csdl/proceedings-article/icse/2024/021700b004/1V5BleCCB56}}.
%   \resumeSubheading
%       {Shah, P., \underline{Pai, K.}, Patel, H., \& Ali, A. (2023).}{}
%       {gem5 Vision}{ISCA 2023: gem5 Workshop.}
%       %Available: \url{https://www.gem5.org/assets/files/workshop-isca-2023/posters/gem5-vision-poster.pdf}}
%   \resumeSubheading
%       {\underline{Pai, K.}, Qiu, Z., \& Lowe-Power, J. (2023).}{}
%       {Validating Hardware and SimPoints with gem5: A RISC-V Board Case Study}{ISCA 2023: gem5 Workshop.}
%       % Available: \url{https://www.gem5.org/assets/files/workshop-isca-2023/posters/validating-hardware-and-simpoints-with-gem5-poster.pdf}}
% \resumeSubHeadingListEnd

% \section{Research Experience}
% \resumeSubHeadingList

% \resumeSubHeadingListEnd

\section{Work Experience}
\resumeSubHeadingList
    \resumeSubheading
        {Graduate Student Researcher}{Jun 2023 - Present} % driving to results, is better than activity, highest goals.
        % top spin, prepare undergrads for undergrad research
        {DArchR Lab @ University of California, Davis}{Davis, CA}
        \resumeSubHeadingList
        %   \resumeItem{\textbullet\ Working with Prof. Jason Lowe-Power on computer architecture research.}
            \resumeItem{\textbullet\ Leading a project to achieve 10x acceleration in the simulation of cryogenic semiconductor computing and superconductors.}
            \resumeItem{\textbullet\ Collaborating with 3 researchers to develop and deliver 90\% correlation between gem5 simulation and hardware measurements.} % develop and deliver 90\% correlation between gem5 simulation and actual hardware measurements by 3-6 months.
            \resumeItem{\textbullet\ Mentoring 5 undergraduate students in the Davis Computer Architecture Lab to prepare them for graduate research.}
    \resumeSubHeadingListEnd
  \resumeSubheading
      {Teaching Assistant}{Sep 2023 - Dec 2023}
      {University of California, Davis}{Davis, CA}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Assisted 180 students in understanding course material and assignments, conducted weekly office hours, and gave and graded assignments for senior-level Probability \& Statistical modeling class.}
        %   \resumeItem{\textbullet\ Conducted weekly office hours and provided feedback on student assignments.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Software Developer Intern \& Tech Lead}{Jan 2022 - Jun 2022}
      {humanID}{Davis, CA}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Delivered 10 completed projects with global teams, including documentation of a Discord bot that combats spam and fake users, and a Django-based web application for permission management for 100 users.} % including documentation of a Discord bot that combats spam and fake users, and a Django-based web application for permission management for 100 users.}
        %   \resumeItem{\textbullet\ Co-created documentation on the implementation of a Discord bot that combats spam and fake users.}
        %   \resumeItem{\textbullet\ Algorithmically hierarchized 100 users and their associated permissions in a Django-based web application.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Technical Product Marketing Intern}{Jul 2021 - Sep 2021}
      {SiTime Corporation}{Santa Clara, CA}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Presented strategy to better distributor margin management and improve earned profits by \$250,000.} % through better distributor margin management.
          \resumeItem{\textbullet\ Conducted a market survey on types of optical transceivers used in AI networking infrastructure, to identify potential customers for MEMS timing chips.} % top spin, conducted a market survey on types of optical transceivers used in AI netwroking infrastructure, to identify potential customers for SiTime's chips.
          \resumeItem{\textbullet\ Created Visio diagrams for the product requirements document for a timing chip.} %
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

% \section*{Summary}
% Passionate AI/ML engineer with a strong background in deep learning, computer vision, and natural language processing. Skilled in Python, TensorFlow, PyTorch, and various ML libraries. Excellent problem-solving, research, and collaboration abilities. Seeking a challenging role to develop cutting-edge AI solutions.

\section{Projects}
\resumeSubHeadingList
  \resumeSubheading{\href{https://www.kunpai.space/assets/papers/prompting.pdf}{Automated Frameworks of Semantic Augmentation to Improve MWP Solving}}{Apr 2024 - Jun 2024}
  {Machine Learning Project}{Python, NLP, Prompt Engineering}
  \resumeSubHeadingList
      \resumeItem{\textbullet\ Improved language model accuracy on MWPs by 10\% (prompting PaLM2) and 60\% (finetuning TinyLlama) through a one-shot digit-level semantics framework, over base model performance.}
      \resumeItem{\textbullet\ Introduced a novel demonstration selection model to identify the most similar equations for one-shot examples using BLEU scores and Levenshtein distance.}
      %\resumeItem{\textbullet\ Utilized BLEU scores and Levenshtein distance in a demonstration selection algorithm and a prompt selection model to identify the most similar equations for one-shot examples, optimizing prompt accuracy.}
      %\resumeItem{\textbullet\ Fine-tuned TinyLlama and prompted PaLM2 with prompt-enhanced GSM8K questions, resulting in improved accuracy on the SVAMP dataset and uncovering insights into the varying context requirements of different mathematical operations.}
      %\resumeItem{\textbullet\ Fine-tuned TinyLlama and prompted PaLM2, boosting SVAMP accuracy and uncovering operation-specific context needs.}
  \resumeSubHeadingListEnd
  \resumeSubheading{\href{https://www.kunpai.space/assets/papers/toxicity.pdf}{Effects of Toxicity on Disengagement in Open Source Projects}}{Jan 2024 - Mar 2024}
  {Software Engineering Project}{Python, GitHub mining, scikit-learn}
  \resumeSubHeadingList
      \resumeItem{\textbullet\ Analyzed factors contributing to developer disengagement in open-source projects, identifying a 0.76 R-squared value between less toxicity and large codebase size with high engagement for FAANG projects.}
      \resumeItem{\textbullet\ Quantified toxicity across corporate and non-profit open-source communities, categorizing comments and examining how toxic interactions disproportionately affected new developers compared to experienced ones.}
    %   \resumeItem{\textbullet\ Proposed community-driven policies and practical implications for project maintainer aiming to mitigate negative interactions and enhance collaborative practices in open-source environments.}
  \resumeSubHeadingListEnd
  \resumeSubheading{\href{https://www.kunpai.space/assets/papers/spectre.pdf}{Behavior of Spectre in Different Branch Predictors in gem5}}{Oct 2023 - Dec 2023}
  {Computer Architecture Project}{C++, gem5}
  \resumeSubHeadingList
      \resumeItem{\textbullet\ Investigated susceptibility of x86-based in-order and out-of-order processors to Spectre V1 attacks using gem5 v23.0, identifying a strong correlation between Spectre attack effectiveness and branch predictor type.}
      \resumeItem{\textbullet\ Proposed design enhancements for a Spectre-resistant branch predictor, emphasizing longer training periods and mitigation of biased branches, aimed at reducing susceptibility to speculative execution attacks.}
  \resumeSubHeadingListEnd
  \resumeSubheading
      {\href{https://resources.gem5.org/}{gem5 Vision}}{Jan 2023 - Jun 2023}
      {Framework}{Next.js, Python, MongoDB, JSON Schema}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Boosted resource discovery speed by 20x with optimized search functionality across 1,200+ resources.}
          \resumeItem{\textbullet\ Introduced semantic versioning and built a categorization system, enabling faster retrieval of resources across 20+ categories.}
          \resumeItem{\textbullet\ Integrated local/remote JSON files and MongoDB for gem5, enhancing accessibility for 500+ users.}
      \resumeSubHeadingListEnd
%   \resumeSubheading
%       {UNIfy - Course Assistant}{Jan 2022 -- Jan 2022}
%       {Hackathon Project}{Python, JavaScript, Discord API}
%       \resumeSubHeadingList
%           \resumeItem{\textbullet\ Utilized the UC Davis Schedule Builder API to extract class timings and professors.}
%           \resumeItem{\textbullet\ Formulated a class-based hierarchized dictionary to maintain schedules of over 100 server members in five Discord servers.}
%           \resumeItem{\textbullet\ Extracted data from APIs of Rate My Professor and Google Calendar to add additional features to the bot.}
%       \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Publications} % switch order, fit in full name of conferences
\resumeSubHeadingList
  \resumeSubheading
      {\href{https://arxiv.org/pdf/2402.02047}{Calibration and Correctness of Language Models for Code}}{Spiess, C., Gros, D., \underline{Pai, K.}, et. al.}
      {International Conference on Software Engineering (ICSE) 2025.}{}
  \resumeSubheading
      {\href{https://dl.acm.org/doi/pdf/10.1145/3597503.3639183}{Automatic Semantic Augmentation of Language Model Prompts (for Code Summarization)}}{Ahmed, T., \underline{Pai, K.}, et. al.}
      {International Conference on Software Engineering (ICSE) 2024.}{}
  \resumeSubheading
      {\href{https://arch.cs.ucdavis.edu/simulation/2024/08/06/potentiallimitationhighfreqcorescaches.html}{Potential and Limitation of High-Frequency Cores and Caches}}{\underline{Pai, K.}, Nand, A. \& Lowe-Power, J.}
      {ModSim 2024 : Workshop on Modeling \& Simulation of Systems and Applications}{}
  \resumeSubheading
      {\href{https://www.gem5.org/assets/files/workshop-isca-2023/posters/gem5-vision-poster.pdf}{gem5 Vision}}{Shah, P., \underline{Pai, K.}, et. al.}
      {gem5 Workshop at International Symposium on Computer Architecture (ISCA) 2023.}{}
  \resumeSubheading
      {\href{https://www.gem5.org/assets/files/workshop-isca-2023/posters/validating-hardware-and-simpoints-with-gem5-poster.pdf}{Validating Hardware and SimPoints with gem5: A RISC-V Board Case Study}}{\underline{Pai, K.}, Qiu, Z., \& Lowe-Power, J.}
      {gem5 Workshop at International Symposium on Computer Architecture (ISCA) 2023.}{}
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingList
    \resumeItem{\textbf{Programming Languages}: Python, C++, Java, JavaScript}
    \resumeItem{\textbf{Frameworks}: React, Next.js, TensorFlow, PyTorch, Django, Flask}
    \resumeItem{\textbf{Tools \& Technologies}: Git, Docker, MongoDB, gem5}
\resumeSubHeadingListEnd

% \section{Certifications}
% \resumeSubHeadingList
%   \resumeItem{\textbullet\ AWS Certified Machine Learning - Specialty}
%   \resumeItem{\textbullet\ TensorFlow Developer Certificate}
% \resumeSubHeadingListEnd

\end{document}